{\centering
\LARGE
Acknowledgements
\par
}

I would like to thank my advisor, Carol Mason, for her guidance, sharing her knowledge, and her warm and enthusiastic encouragement throughout my time as a student, even before I joined her lab.
She has helped me nurture and develop my love of using detailed anatomical approaches and careful observations to understanding the brain.
%It was this shared appreciation that first drew me to her lab, and I'm grateful for having been able to conduct research in this vein in an environment where it is celebrated and appreciated.
I have grown tremendously as a scientist in her lab, and I am very grateful for the opportunities she has given me and helped me to cultivate on my own.

Carol has a remarkable knack for filling her lab with deeply kind, good-natured people, and it has made working in her lab a real joy.
Rich, with whom I've sat back-to-back in our shared bay, has been a source of thoughtful conversation, lighthearted joking, mutual understanding, and trading cat stories.
He also contributed a great deal to EM efforts, and I am grateful for all of his work and for always fixing things in lab.
Mika is one of the kindest people I've met, and incredibly hard working.
I'm appreciative of all her work in the lab, including the little things that make it a better place to work, like keeping the plants alive and frequently bringing in baked goods.

I've had the honor of sharing my time in the lab with several talented, bright postdocs and students.
Alex trained me when I was just starting out in Carol's lab, and I learned a lot from her in a relatively short amount of time.
She continues to be a valuable source of input and guidance from afar.
Taka, a really fabulous scientist and person, also trained me.
I will remember not only the \invitro{} techniques he expertly taught me, but also the many delightful life conversations we shared.
Florencia, Jeanette, and Lena have been wonderful sources of knowledge, guidance, and friendship.
Punita and Qing both took me under their wings when I joined the lab and have continued to be a great source of support even after they left the lab.
It has also been a pleasure to work with and cultivate friendships with Celia, Raven, Anna, and Melissa.
It's been exciting to be part of Melissa's training in the Mason Lab and I'm excited to see where her project and career take her.
Emily was a pleasure to work with and also helped pilot \invitro{} experiments.
Nick also contributed to the \invitro{} work as a rotation student, and even though the automated analysis didn't work out, his efforts are much appreciated.
Felix has been a fantastic collaborator on the Y assay, and I am much indebted to him for his help.
I also appreciate the hard work and good company from the many undergraduate and high school students, particularly Sophie, Claire, Irene, Sania, and Rehnuma.

My committee members, Wes, Jane, and Ulrich, have provided input to this project, and I am grateful for their insights, questions, and critiques along the way, which helped me develop into a better independent scientist.
Ulrich's feedback often helped me view things in a new way, and I appreciate the opportunity to develop this skill. 
Wes has been a reliable, valuable, and much appreciated source of support, encouragement, and advice.
Jane's scientific thoughtfulness, insight, rigor, and candor have been incredibly instructive, and I am grateful for her guidance and support.
The Neurobiology and Behavior Program administrators and co-directors have been helpful over the years.
Additionally, Tania in the Advanced Instrumentation Core and Theresa in the Confocal and Specialized Microscopy Core provided valuable technical assistance.

I am also much indebted to my previous mentors, Theresa, Alan, and Annmarie, as well my rotation advisors, Ai and Fiona, all of whom have contributed to my development as a scientist and provided valuable training and perspectives.
I am incredibly lucky to have had such an amazing group of friends during my PhD who have provided guidance, support, and truly fantastic examples, both in career and life - Cate, Kara, Becky, Lizzie, Heather, Megan, Kelley, Alyssa, Flo, Bethany, Betsy, Heidi, Nancy, Tracy, Liz, Stephanie, Ben and Amy, and many other students at Columbia who have been good friends and colleagues.
This journey was greatly improved by my friends' company and the many wine nights spent together sharing stories, advice, and laughter.
Finally, I am grateful for the love and support from my family.
They provided me not only with encouragement, but the tenacity, stubbornness, attention to detail, and work ethic necessary for my scientific career.
And, of course, I am deeply grateful for Joe, his patience and love, good humor, support and encouragement, and cats.
He also assisted with compiling the thesis into \LaTeX, got me to start using GitHub, and wrote the python code for some statistical analyses.