After observing that 20$\mu$m cryosections of embryonic mouse brain became transparent in the hybridization buffer used for \emph{in situ} hybridization, we found that a component of the buffer, formamide, could clear thick tissue samples.
Here, we demonstrate the versatility of our method, named \emph{Clear\textsuperscript{T}} for neuronal and non-neuronal tissue, and compare its clarity, rapidity, and tissue expansion/shrinkage to existing clearing methods.

Intact embryos, embryonic and postnatal dissected heads, brains, and thick (up to 1000$\mu$m) brain sections, were fixed and sequentially immersed in graded concentrations of formamide (Table~\ref{ClearT.tgn}, Fig. 1A).
%Fix fig
\begin{table}[hbtp]
    \begin{center}
        \includetable{80_Appendix2_ClearT/ClearT.tgn}
        \caption[Clearing Procedures.]
        {Clearing Procedures.
		A) Clearing protocol for various sample types using \emph{Clear\textsuperscript{T}}.
		B) Clearing protocol for various sample types using \emph{Clear\textsuperscript{T2}}.
		}
        \label{ClearT.tgn}
    \end{center}
\end{table}
The \emph{Clear\textsuperscript{T}} procedure rendered embryonic brains as transparent as with Sca\emph{l}eA2, but did so significantly faster (1 day versus 14 days) (Fig. 1B).
Completely cleared postnatal day 0 (P0) brain sections were similar to their original size (before clearing=1.0\pm0 versus \emph{Clear\textsuperscript{T}}=1.04\pm0.02, not significant, n=6 sections) (Fig. 1C).
%Fix fig
Even after prolonged treatment with {Clear\textsuperscript{T}}, sample volume only increased slightly, significantly less than in Sca\emph{l}eA2 [1 day, {Clear\textsuperscript{T}}=1.33\pm0.09 versus Sca\emph{l}eA2=1.81\pm0.05, P<0.01; 2 days, {Clear\textsuperscript{T}}=1.27\pm0.09 versus Sca\emph{l}eA2=1.83\pm0.06, P<0.01, n=5 ({Clear\textsuperscript{T}}), 4 (Sca\emph{l}eA2) sections] (supplementary material Fig. S1).
%Fix fix
Although formamide is not harmful to tissue in the short term, it is unsuitable for long-term tissue storage.
Therefore, we transferred samples treated with {Clear\textsuperscript{T}} into PBS, where they became opaque within 30 minutes and could be safely stored for at least 1 month (Fig. 1D).
%Fix fig