Despite the fact that fasciculation has long been considered a fundamental mechanism of neural circuit development (reveiwed in \cite{raper2010cellular,wang2013axons}, our understanding of the mechanisms underlying axon-axon interactions and how they contribute to sorting of axons in tracts remains limited.
In their review of axon-axon interactions, Wang and Marquardt (2013) offer an insightful distinction between homotypic and heterotypic axon fasciculation, which we will similarly use to guide the present review of axon-axon interactions involved in pre-target axon organization. 
We first consider homotypic fasciculation situations where like axons, those of the same source or subset, are joined together by adhesive forces or corralled together by surround repulsion.

Fasciculation of homotypic axons has been studied most commonly in the pioneer-follower model of early tract formation. 
Pioneer axons provide a path along which younger axons follow, but while loss of pioneer axons often disturbs tract formation, follower axons in some systems can successfully navigate to their targets in the absence of pioneers \cite{raper2010cellular}.
An elegant set of experiments in the developing zebrafish retinotectal system provides a case in which pioneer RGC axons are both necessary and sufficient for leading later-born RGC axons along the correct path to the optic tectum \cite{pittman2008pathfinding}.
The results of this study also imply that pioneer-follower RGC axon-axon interactions trump extra-axonal cues along the tract.
Transplanting mutant pioneer RGCs from zebrafish lacking the Slit receptor Robo2 into wt retinae caused wt axons to make routing errors alongside transplanted mutant pioneers.
Conversely, transplanting wt pioneer RGCs into mutant retinae rescued many host axons from making pathfinding errors \cite{pittman2008pathfinding}.
These results advocate for the importance of direct axon-axon interactions in generating organized vertebrate axon tracts.
Slit and Robo are also involved in motor axon fasciculation in the mouse, where Slit2 directly promotes fasciculation via interactions with Robo1 and Robo2 by an autocrine/juxtaparacrine mechanism \cite{jaworski2012autocrine}.

Surround repulsion can also lead to homotypic fasciculation by corralling like axons together away from external repulsive signals.
Despite the fact that such surround-repulsion scenarios result from extra-axonal cues, we consider them in this section, as an increase in homotypic fasciculation is the end result.
For instance, motor axons expressing Nrp1 fasciculate via surround repulsion from Sema3A in the mouse forelimb.
In the absence of Sema3A, motor axons defasciculate and subsequently make errors in dorsal-ventral pathfinding in the limb plexus region \cite{huber2005distinct}.
On the other hand, Sema3F-Nrp2 interactions do not affect fasciculation of motor axons in the limb \cite{huber2005distinct}.
They do, however, drive fasciculation of vomeronasal axons in the murine accessory olfactory system, although they are not involved in pathfinding in this system \cite{cloutier2002neuropilin}.

The Eph:ephrin family of cell surface proteins is also involved in mediating selective homotypic fasciculation of axon cohorts via selective surround repulsion.
EphB2-expressing sensory and motor axons fasciculate via surround repulsion from ephrin-B1 produced in the limb bud mesenchyme.
Ephrin-B1 expression on sensory axons indicates a more complicated interaction may be involved in addition to the surround-repulsion from the mesenchyme \cite{luxey2013eph}.
Loss of ephrin-B1 in mice leads to defasciculation of axon tracts, especially the oculomotor nerve \cite{davy2004ephrin}; and in double knockout mutants lacking both EphB2 and EphB3, axons extending from the habenular nuclei extensively defasciculate.
Fasciculation is normal, however, in each single knockout mutant \cite{orioli1996sek4}.
Whether appropriate maintenance of homotypic fasciculation is necessary for appropriate innervation and synaptogenesis in the target remains to be elucidated.


Heterotypic axon-axon interactions

Axon cohorts in tracts can be either grossly or finely heterotypic.
This section will first consider grossly heterotypic axon-axon interactions, prime examples of which include TCAs and CTAs in the thalamocortical tract, or sensory and motor spinal axons in the periphery, where two cohorts from different sources run segregated from each other in a tract containing reciprocal projections.
Finely heterotypic axon-axon interactions are those occurring between subsets of axons arising from the same source but representing different molecularly defined neuronal subtypes; these cases will be considered at the end of this section.
Common guidance molecules participate in both types of heterotypic axon-axon interactions, including the Eph:ephrin family, Semas, Plexins, and Neuropilins. 

In the peripheral nerve tracts, motor axons extend before sensory axons, which in turn rely on motor axons to form correct patterns of connections \cite{wang2013axons}.
While these two heterotypic axon cohorts run closely together, sensorimotor function requires their appropriate segregation.
In the axial nerves, this segregation has been found to depend on repulsive trans-axonal signaling between motor axon EphA3/EphA4 receptors and sensory axon ephrin-A ligands.
Perturbing ephrinA-EphA forward signaling accordingly results in severe wiring defects in the peripheral nerves \cite{gallarda2008segregation}.
However, EphA3/4 and ephrin-As are also required for sensory axons to track along preformed motor axon pathways in the limb \cite{wang2011anatomical}.
This curious dual action of EphAs/ephrin-As relies on the forward and reverse signaling capabilities of the binding partners; namely, segregation of motor and sensory axons results from forward signaling and sensory axon tracking along motor axons utilizes reverse signaling \cite{wang2011anatomical}.
The reliance on motor axons for sensory axon pathfinding was further demonstrated by assessing the sensory axon routes taken in two mouse strains that display motor axon pathfinding errors (EphA4 and Ret mutants).
In both cases, as well as in analogous zebrafish mutants, sensory axons mimicked the pathfinding errors made by motor axons \cite{wang2014conserved}. 

The reciprocal projections comprising the thalamocortical pathway are the other prime example of grossly heterotypic axon-axon interactions in developing tracts.
Recent work demonstrates a mutual reliance of TCAs and CTAs on each other for successful tract organization and navigation to their respective targets (e.g. \cite{chen2012evidence,deck2013pathfinding}, and some of the molecules involved in these axon-axon interactions have been identified.
The CTA waiting period, as discussed previously, is governed by Sema3E/Plexin-D1.
If Sema3E/Plexin-D1 signaling is perturbed, all corticofugal axons pass the PSPB prematurely, bypassing their encounter with TCAs.
They subsequently take a cortico-subcerebral trajectory, rather than dividing into the appropriate corticothalamic and cortico-subcerebral paths \cite{deck2013pathfinding}.
This finding highlights the necessity of the subpallial “handshake” between thalamic and cortical axons.
In the converse scenario, when CTA outgrowth is prevented, TCAs are rendered incapable of navigating across the PSPB and into the cortex \cite{chen2012evidence}.
This mutual reliance is suggestive of heterotypic axon-axon interactions or fasciculation occurring in the PSPB and along the tract.
Curiously, TCAs and CTAs collapse upon contact with each other in vitro, and thus are not intrinsically inclined to co-fasciculate \cite{bagnard2001axonal}.
From this, the “handshake” between TCAs and CTAs is likely mediated by a combination of axon-extrinsic cues in the surrounding ventral telencephalon, which may in turn affect direct axon-axon interactions between the two axon populations.
The intimate association between thalamic and cortical axons in the IC and along the tract \cite{molnar1998mechanisms} implicates cofasciculation between these heterotypic axon cohorts.
Likewise, their codependency on each other for guidance, and the fact that a subset of CTAs track along misrouted TCAs in EphB1/2 double knockout mice \cite{robichaux2014ephb}, provides further support to a model in which direct axon-axon interactions are involved in organization and guidance of these axonal cohorts.

The Eph:ephrin family may be involved in such an interaction.
In the primary olfactory nerve of the moth Manduca sexta, Eph receptors and ephrins are differentially expressed among glomeruli and are candidates for mediating OSN axon sorting prior to glomerulus innervation \cite{kaneko2003interaxonal}.
Importantly, there is no detectable Eph or ephrin expression intrinsic to the OSN axons’ target, the antennal lobe, signifying that Eph-ephrin repulsive signaling involved in sorting axons would necessarily occur via direct axon-axon interactions \cite{kaneko2003interaxonal}.

Eph-ephrin mediated sorting of moth OSN axons involves a different kind of heterotypy than has been considered thus far.
As opposed to the grossly heterotypic interactions of reciprocal projections in the spinal cord or thalamus, in finely heterotypic axon-axon interactions, axons originating from the same source must segregate into appropriate sub-fascicles representing different neuronal subtypes prior to target innervation.
Sorting of axons into sub-fascicles in a tract is thought to occur by selective inhibition of fasciculation, such that individual cohorts can separate from a larger group and select the correct trajectory to the appropriate target.
An example comes from the chick spinal cord marginal zone, where intermediate and medial longitudinal commissural (ILc and MLc) axons run parallel in the lateral and ventral funiculi, respectively.
ILc axons express Robo, which is thought to inhibit N-cadherin-driven fasciculation in order to separate ILc axons away from the MLc fascicle.
Accordingly, loss of Robo function leads to ILc axons aberrantly coursing alongside MLc axons in the ventral funiculus and subsequently mistargeting in the brain \cite{sakai2012axon}.

Semas and their Nrp and Plexin receptors are also involved in sorting axons within tracts.
In the mouse OE, different populations of OSN axons express Sema3A and Nrp1 in a roughly regionally defined manner.
These OSN axons are likewise segregated from each other in the olfactory nerve, and selectively deleting either Nrp1 or Sema3A in OSNs leads to a blurring of pre-target axon order and shifts in glomerular position in the OB \cite{imai2009pre}.
Because these effects are found in conditional mutants that only affect subsets of OSNs, they occur independently of Sema3A surround expression by OEG.
Given this result, the authors conclude that axon-axon interactions are critical for establishing pre-target axon organization in the olfactory nerve \cite{imai2009pre}.

Sema3A and Nrp1 are also implicated in establishing the dorsal-ventral segregation of axons in the CC \cite{zhou2013axon}.
This order reflects a medial-high to lateral-low gradient of Nrp1 expression in the cortex and a reciprocal, though broader expression of Sema3A, which is slightly higher in the lateral cortex.
Disrupting these molecular gradients perturbs both axon position in the CC and the position of axon terminations in the contralateral cortex.
The authors propose that both axon-extrinsic and axon-axon interactions are at play \cite{zhou2013axon}.
It is intriguing to speculate that Sema/Nrp interactions may be a conserved mechanism in mediating axon sorting across other systems as well.