The following primary antibodies were used:
\begin{itemize}
	\item[-] rabbit polyclonal anti-zsgreen antibody, Clontech (catalog no. 632474), used at 1:500
	\item[-] rabbit polyclonal anti-laminin (Invitrogen, catalog no. PA1-84171), used at 1:500
	\item[-] chicken polyclonal anti-GFP, Abcam, used at 1:500
	\item[-] rat anti-mCherry, Abcam, used at 1:1000 %(check manufacturer)
	\item[-] mouse monoclonal anti-neurofilament (IgG) antibody (2H3), a gift from T. Jessell and S. Morton, Columbia University, NY, USA, used at 1:5
	\item[-] rabbit anti-Zic2 (gift from Stephen Brown, University of Vermont), used at 1:10,000
	\item[-] mouse monoclonal anti-Islet1/2 (4D5), gift from T. Jessell and S. Morton, used at 1:50
\end{itemize}

The following secondary antibodies were used:
\begin{itemize}
	\item[-] goat anti-mouse AlexaFluor 488, 594, or 647, Invitrogen, used at 1:400
	\item[-] goat anti-rabbit AlexaFluor 488 or 594, Invitrogen, used at 1:400
	\item[-] goat anti-chicken AlexaFluor 488, Invitrogen, used at 1:400
	\item[-] donkey anti-rabbit AlexaFluor 350, Invitrogen, used at 1:400
	\item[-] donkey anti-rat AlexaFluor 594, Invitrogen, used at 1:400
\end{itemize}
Where Hoechst was used, it was applied at RT at a concentration of 1:5,000 in PBS, for 10-20 minutes (min), after secondary antibody application, and then rinsed three times with 1X PBS.

\noindent\textbf{Immunostaining of retinal explants} \newline
\indent Explant cultures were fixed with warm 4\% PFA in 1X PBS or warm 4\% PFA + 0.1\% glutaraldehyde in 10\% sucrose/PBS solution, for 15-20 min at RT, then rinsed 2-3 times with RT 1X PBS.
Fixed cultures were incubated for 45-90 min at RT in blocking solution composed of 1X PBS + 1\% Triton X-100 + 10\% normal goat serum (NGS).
Primary antibodies were applied in a 1X PBS + 1\% Triton X-100 + 5\% NGS solution and incubated O/N at 4\textcelsius.
The following day, samples were rinsed for 15-30 min three times with 1X PBS at RT.
Secondary antibodies were applied in a 1X PBS + 1\% Triton X-100 + 5\% NGS solution and incubated at RT for 2-4 hours (h).
Samples were rinsed three times and coverslips mounted onto slides with Fluoro-Gel mounting medium (Electron Microscopy Sciences).

\noindent\textbf{Immunostaining of zsgreen in vibratrome sections with DiD label} \newline
\indent After anterograde labeling with DiD, brains were sectioned 50 $\mu$m thick and collected into wells of 1X PBS.
Free floating sections were incubated for 60-90 min at RT in blocking solution composed of 1X PBS + 0.25\% Tween 20 (Sigma-Aldrich) + 10\% NGS.
Primary antibodies were applied in a 1X PBS + 0.25\% Tween 20 + 5\% NGS solution and incubated for 2 nights at 4\textcelsius.
Samples were then rinsed 20-30 min 3 times with 1X PBS, and then secondary antibodies were applied in a 1X PBS + 0.25\% Tween 20 + 5\% NGS solution and incubated for 3-4 h at RT.
Samples were rinsed once with 1X PBS, incubated with Hoechst for 10-20 min, then rinsed three times with 1X PBS, and mounted sequentially and coverslipped with Fluoro-Gel mounting medium.

\noindent\textbf{Immunostaining of cryosections} \newline
\indent Cryosections 25 $\mu$m thick were collected in sequence in 4 parallel series of slides.
One or two sets were immunostained and imaged, resulting in serial sections either 100 $\mu$m or 50 $\mu$m apart, respectively.
Slides with cryosections were brought to RT from -80\textcelsius{} and left to dry before being rinsed with 1X PBS once for 5-10 min.
Samples were incubated for 45-90 min at RT with blocking solution composed of 1X PBS + 0.5\% Tween + 10\% NGS.
Primary antibodies were applied in a 1X PBS + 0.5\% Tween 20 + 10\% NGS solution and incubated for 2 nights at 4\textcelsius.
Samples were then rinsed for 15-20 min three times with 1X PBS, then secondary antibodies were applied in a 1X PBS + 0.5\% Tween 20 + 5\% NGS solution and incubated for 3-4 h at RT.
Samples were rinsed once with 1X PBS, incubated with Hoechst for 10-20 min, then rinsed three times with 1X PBS, and coverslipped with Fluoro-Gel mounting medium.